wgcna

### 2019-08-23 analysis/08_wgcna.Rmd
documentation

**Fig 1. Characterization dendrogram with trait heatmap.**. 
 Most hyp. and pit. samples separte form the gon. samples, but some are clusters contain samples from all tissues.

@@

**Fig 2. Female characterization dendrogram with trait heatmap.**. 
Most pit samples form a single cluster. More hyp samples cluster with gonads than with pituitary.

@@

**Fig 3. Male characterization dendrogram with trait heatmap.**. 
 As with females, most pit samples form a single cluster, and More hyp samples cluster with gonads than with pituitary.

>>>>

**Fig 1. Characterization dendrogram with trait heatmap.**. 
 Most hypothalamus and pituitary samples separte form the gonad samples, but some are clusters contain samples from all tissues.

@@

**Fig 2. Female characterization dendrogram with trait heatmap.**. 
Most pituitary samples form a single cluster. More hypothalamus samples cluster with gonads than with pituitary.

@@

**Fig 3. Male characterization dendrogram with trait heatmap.**. 
 As with females, most pituitary samples form a single cluster, while more hypothalamus samples cluster with gonads than with pituitary.
